%--------------------------------------------------------
% BEER PONG RULES: MISCELLANEOUS RULES SECTION
%--------------------------------------------------------
\section{Miscellaneous Rules}\label{sec:Misc}
	\subsection{Glitches in the Matrix}\label{ssec:Glitches}
        \begin{enumerate}[label=(\roman*)]
            \item \label{sec:Misc,onto} If a shot happens to land on top of the cups, that shot will count as a miss.
                Congratulations - you are lucky, but you have not proved that you have any pong skills at all.
            \item \label{sssec:Misc,wind} When playing outside, and a gust of wind comes up and blows the ball causing a miss, that is unfortunate but valid.
                Vice versa for defenders.
        \end{enumerate}
	\subsection{Balling Your Own Cups}\label{ssec:OwnScore}
        \begin{enumerate}[label=(\roman*)]
            \item \label{sssec:OwnScore,penalty} In the event that a player who has possession of the ball, drops a ball into one of their own cups \emph{accidentally} that cup is removed as if a ball was just sunk by opponents. \footnote{This sinking does not count to the on-fire or heating up or double in for the other team.}
            \item \label{sssec:OwnScore,backboard} In the event that a player who does not have possession of the ball comes in contact with the ball and as a result that ball is sunk in of their own cups, such as by unintentionally acting as a backboard, that shot IS counted and the cup is hit.
        \end{enumerate}
	\subsection{During the Game}\label{ssec:DuringGame}
		\begin{enumerate}[label=(\roman*)]
            \item \label{sssec:MaintainRack} During the game, players must maintain their rack.
                This means that they should keep the cups kissing with their neighbours, and two fingers from the edge but no more than 4.
                The remaining cups should be in the places they started the game in unless a valid rerack moved them.
            \item \label{sssec:Knockover} A team member knocking over their own cups also counts as a removal of that cup from the game as if a ball was sunk. no matter the reason.
            \item \label{sssec:swiping_no_bounce} A player that swipes/grabs a ball that has been thrown by the opponent and not yet bounced must then take a cup out of their rack of the opponents choice.
                The ball is not returned to the thrower.
            \item \label{sssec:FinalCountDown} If both sides only have one cup left in their rack, the music must be changed to one of the following songs: The Final Count Down by Europe, Chariots of fire, the pong dance.
            \item \label{sssec:finalSongEnd} If the final song ends (see \hyperref[sssec:FinalCountDown]{Section \ref{sssec:FinalCountDown}}) Then the teams switch sides and play another song listed in. \ref{sssec:FinalCountDown}
        \end{enumerate}